The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-07-26 albatros_paper.tex
HCC fixed accumulation time

A Smart Network ADC Processor~\citep[SNAP;][]{2016JAI.....541001H}
board digitizes the RF signals at 250~Msamp/s and uses a Xilinx
Kintex~7\footnote{\url{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}}
FPGA to calculate full cross-correlations of the four inputs,
producing four auto- and six cross-spectra as outputs, over 2048
channels spanning the frequency range 0--125~MHz.  The channelization
is performed with a
CASPER\footnote{\url{https://casper.berkeley.edu/}}-based polyphase
filter bank, and the spectra are accumulated over $\sim7$-s intervals.
A Valon 5007 frequency synthesizer module provides the clock signal
for the SNAP board.  A Raspberry Pi (RPi)~3B+ single board computer
controls the SNAP board and receives the spectra via GPIO connections.
The data rate of the averaged spectra is roughly 400~MB/day (with
compression), and this low volume allows the spectra to be saved to
the RPi on-board SD card.  An Adafruit Ultimate GPS
module\footnote{\url{https://www.adafruit.com/product/746}}, connected
to an active external GPS antenna, provides absolute timing for the
RPi.

>>>>

A Smart Network ADC Processor~\citep[SNAP;][]{2016JAI.....541001H}
board digitizes the RF signals at 250~Msamp/s and uses a Xilinx
Kintex~7\footnote{\url{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}}
FPGA to calculate full cross-correlations of the four inputs,
producing four auto- and six cross-spectra as outputs, over 2048
channels spanning the frequency range 0--125~MHz.  The channelization
is performed with a
CASPER\footnote{\url{https://casper.berkeley.edu/}}-based polyphase
filter bank, and the spectra are accumulated over $\sim4$-s intervals.
A Valon 5007 frequency synthesizer module provides the clock signal
for the SNAP board.  A Raspberry Pi (RPi)~3B+ single board computer
controls the SNAP board and receives the spectra via GPIO connections.
The data rate of the averaged spectra is roughly 400~MB/day (with
compression), and this low volume allows the spectra to be saved to
the RPi on-board SD card.  An Adafruit Ultimate GPS
module\footnote{\url{https://www.adafruit.com/product/746}}, connected
to an active external GPS antenna, provides absolute timing for the
RPi.
